Deep Reinforcement Learning for Conservation Decisions

### 2021-05-18 manuscript/manuscript.Rmd
Adding to the table

The reinforcement learning problem is typically formalized as a partially observable Markov decision process (POMDP).
A POMDP is a 7-tuple that consists of the following: 
- $\mathcal{S}$: a set of states called the state space
- $\mathcal{A}$: a set of actions called the action space
- $\Omega$ : a set of observations called the  observation space
- $E(o_{t}| s_{t})$: an emission distribution, which accounts for an agent's observation being different from environment's state
- $T(s_{t+1}|s_t, a_t)$: a state transition operator which describes the dynamics of the system
- $r(s_t, a_t)$: a reward function
- $d_0(s_0)$: an initial state distribution
- $\gamma \in (0,1]$: a discount factor

@@

Note that this formalism extends to an infinite horizon case when $T= \infty$.
While there are RL methods to deal with infinite horizon cases, we will only present methods for finite horizon or episodic MDP and POMDPs.

@@

Over the course of training, RL agents will engage in trial and error learning, whereby it will be necessary for the agent to explore new sequences of actions as well as exploit past high rewarding sequences.
Occasionally, the agent will need to propose exploratory actions that may result in higher rewards than previously seen. 
Yet, the agent may also need to focus on past sequences of actions which may require marginal improvement to reach optimality.
The fundamental issue is that it is very difficult for the agent to know when it should engage in explorative or exploitative behavior. 
This *exploration-exploitation dilemma* is an open research problem [@berger-tal_exploration-exploitation_2014], and current deep RL algorithms take a range of approaches towards this dilemma -- in the appendix, we discuss some of the more specific exploration algorithms.
Yet, generally, the manner in which RL algorithms explore depend on whether the algorithms are *on-policy* or *off-policy*.
The distinction between on and off-policy exploration comes from what policy the agent is using to select actions during training.
For off-policy algorithms, the agent uses a policy during training that can be different from the policy that the agent will use during evaluation; while in on-policy algorithms, the agent uses the same policy in training as the agent will use during evaluation.
There are trade-offs to consider in using an off-policy or on-policy learner, which we will further discuss in the appendix.

@@

-->
```{=latex}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Algorithm & Description & Model & Evaluation & Policy & Constraints  \\
\hline
MBPO & Model-based Policy Optimization [@mbpo] & Model-based & On-policy & Deterministic & \\
\hline
MCTS & Monte Carlo Tree Search [@suttonbarto] & Model-based & Either & & \\
\hline
A2C  & Advantage Actor Critic [@a2c] & Model-free & On-policy& &\\
\hline
A3C  & Asynchronous A2C & Model-free [@a3c] & On-policy & &\\
\hline
TRPO  & Trust Region Policy Optimization [@trpo] & Model-free & On-policy & &\\
\hline
PPO  & Proximal Policy Optimization [@ppo] & Model-free & On-policy & &\\
\hline
DQN & Deep Q Networks [@dqn] & Model-free & Off-policy& &\\
\hline
DDPG & Deep Deterministic Policy Gradient [@ddpg] & Model-free & Off-policy & &\\
\hline
TD3 & Twin Delayed DDPG [@td3] & Model-free & Off-policy & &\\
\hline
SAC & Soft Actor Critic [@sac] & Model-free & Off-policy & &\\
\hline
IMPALA & Importance Weighted Actor Learner [@impala] & Model-free & Off-policy & &\\
\hline
APE-X & Distributed Prioritized Experience Replay [@apex] & Model-free & Off-policy & & \\
\hline
\end{tabular}
\end{center}
```
# Examples

>>>>

The reinforcement learning problem is typically formalized as a discrete-time partially observable Markov decision process (POMDP).
A POMDP is a 7-tuple that consists of the following: 
- $\mathcal{S}$: a set of states called the state space
- $\mathcal{A}$: a set of actions called the action space
- $\Omega$ : a set of observations called the  observation space
- $E(o_{t}| s_{t})$: an emission distribution, which accounts for an agent's observation being different from environment's state
- $T(s_{t+1}|s_t, a_t)$: a state transition operator which describes the dynamics of the system
- $r(s_t, a_t)$: a reward function
- $d_0(s_0)$: an initial state distribution
- $\gamma \in (0,1]$: a discount factor

@@

Note that this formalism extends to an infinite horizon case when $T= \infty$.
While there are RL methods to deal with infinite horizon cases, we will only present methods for finite horizon or episodic POMDPs.

@@

Over the course of training, RL agents will engage in trial and error learning, whereby it will be necessary for the agent to explore new sequences of actions as well as exploit past high rewarding sequences.
Occasionally, the agent will need to propose exploratory actions that may result in higher rewards than previously seen. 
Yet, the agent may also need to focus on past sequences of actions which may require marginal improvement to reach optimality.
The fundamental issue is that it is very difficult for the agent to know when it should engage in explorative or exploitative behavior. 
This *exploration-exploitation dilemma* is an open research problem [@berger-tal_exploration-exploitation_2014], and current deep RL algorithms take a range of approaches towards this dilemma -- in the appendix, we discuss some of the more specific exploration algorithms.
Yet, generally, the manner in which RL algorithms explore depend on whether the algorithms are *on-policy* or *off-policy*.
The distinction between on and off-policy evaluation comes from what policy the agent is using to select actions during training.
For off-policy algorithms, the agent uses a policy during training that can be different from the policy that the agent will use during evaluation; while in on-policy algorithms, the agent uses the same policy in training as the agent will use during evaluation.
There are trade-offs to consider in using an off-policy or on-policy learner, which we will further discuss in the appendix.

@@

-->
```{=latex}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Algorithm & Description & Model & Method & Evaluation  & Constraints  \\
\hline
MBPO & Model-based Policy Optimization [@mbpo] & Model-based & Planning & On-policy & \\
\hline
MCTS* & Monte Carlo Tree Search [@suttonbarto] & Model-based & Planning & Either & Not suited for continuous action and state spaces \\
\hline
A2C  & Advantage Actor Critic [@a2c] & Model-free & Actor Critic  & On-policy & \\
\hline
A3C  & Asynchronous A2C [@a3c] & Model-free & Actor Critic & On-policy & \\
\hline
ACKTR  &  Actor Critic using Kronecker-Factored Trust Region [@acktr] & Model-free & Actor Critic & On-policy & \\
\hline
ACER  &  Actor Critic with Experience Replay [@wang_sample_2017] & Model-free & Actor Critic & Off-policy & Not suited for discrete action spaces \\
\hline
TRPO  & Trust Region Policy Optimization [@trpo] & Model-free & Actor Critic & On-policy & \\
\hline
PPO  & Proximal Policy Optimization [@ppo] & Model-free & Actor Critic & On-policy & \\
\hline
DQN & Deep Q Networks [@dqn] & Model-free & Value-based & Off-policy & Not suited for continuous action spaces; Suffers from overestimation bias\\
\hline
Double DQN & Deep Q Networks [@van_hasselt_deep_2015] & Model-free & Value-based & Off-policy & Not suited for continuous action spaces \\
\hline
DDPG & Deep Deterministic Policy Gradient [@ddpg] & Model-free & Actor Critic & Off-policy & Not suited for discrete action spaces\\
\hline
TD3 & Twin Delayed DDPG [@td3] & Model-free & Actor Critic & Off-policy & Not suited for discrete action spaces \\
\hline
SAC & Soft Actor Critic [@sac] & Model-free & Actor Critic & Off-policy & Not suited for discrete action spaces\\
\hline
IMPALA & Importance Weighted Actor Learner [@impala] & Model-free & Actor Critic & Off-policy & \\
\hline
\end{tabular}
\caption{A survey of popular deep RL algorithms. With the plethora of deep RL algorithms, this table aims to show some of the most common ones. Model-free algorithms are in the majority in this table as the model-free approach has garnered more attention in recent years. Model-based approaches like MCTS, which is the basis for AlphaZero, are still able to achieve state of the art performances on certain tasks, so they should not be overlooked. Despite there being a range of different algorithms in this table, many of them are closely related to one another. E.g. Double DQN makes a small adjustment to DQN; PPO is an evolution of TRPO; TD3 is an evolution of DDPG; and, A2C is marginally different from A3C. These small differences, however, can result in large change in agent performance. All deep RL algorithms have their respective weak points, and it is impossible to know how algorithms will perform on a task until they are tuned and evaluated. As a deep rl practitioner, the best thing to do then is to find a range of algorithms that can work on your problem's state and action space, tune the algorithms, and see how they perform.}
\end{center}
```
# Examples
